\bf Forecast Reconciliation: A geometric view with new insights on bias correction.

### 2019-09-04 Hierarchical-forecast-reconciliation/Appendix.tex
Adding more references and adjusting table in Appendix

	\begin{table}[H]
		\caption{Geographical hierarchy of Australian tourism flow}\label{table:A1}
		\centering\tabcolsep=0.08cm
		\tiny
		\resizebox{\linewidth}{!}{
			\begin{tabular}{lllllllllll}
				\toprule
				\multicolumn{3}{c}{\textbf{Level 0 - Total}}    &&  \multicolumn{3}{l}{\textit{Zones cont.}}   &  & \multicolumn{3}{l}{\textit{Regions cont.}} \\
				\cmidrule(lr){1-3}
				1 & {\text{Tot}} & {Australia}                  && 48  & AED & Blue Mountains && 99 & FAA & Hobert and South\\
				\cmidrule(lr){1-3}
				\multicolumn{3}{c}{\textbf{Level 1 - States}}               && 49  & AFA & Canberra  && 100 & FBA & East Coast\\
				\cmidrule(lr){1-3}
				2 & A & NSW 				&  & 50  & BAA & Melbourne      && 101 & FBB & Launceston, Tamar \& North\\
				3 & B & Victoria 			&  & 51  & BAB & Peninsula      && 102 & FCA & North West\\
				4 & C & Queensland 			&  & 52  & BAC & Geelong        && 103 & FCB& Wilderness West\\
				5 & D & South Australia     &  & 53  & BBA & Western        && 104 & GAA& Darwin\\
				6 & E & Western Australia   &  & 54  & BCA & Lakes          && 105 & GAB& Kakadu Arnhem\\
				7 & F & Tasmania   			&  & 55  & BCB & Grippsland     && 106 & GAC& Katherine Daly\\
				8 & G & Northern Territory &  &  56  & BCD & Phillip Island && 107 & GBA& Barkly\\
				\cmidrule(lr){1-3}
				\multicolumn{3}{c}{\textbf{Level 2 - Zones}}  &  &  57  & BDA & Central Murray && 108 & GBB& Lasseter\\
				\cmidrule(lr){1-3}
				9 	& AA & Metro NSW 	  	   	&  & 58  & BDB & Goulburn && 109 & GBC& Alice Springs\\
				10 	& AB & North Coast NSW 	   	&  & 59  & BDC & High Country && 110 & GBD& MacDonnell\\
				11	& AC & South Coast NSW	   	&  & 60  & BDD & Melbourne East &&&&\\
				12	& AD & South NSW 			&  & 61  & BDE & Upper Yarra &&&& \\
				13	& AE & North NSW 			&  & 62  & BDF & Murray East &&&&\\
				14	& AC & ACT					&  & 63  & BEA & Wimmera+Mallee &&&&\\
				15	& BA & Metro VIC			&  & 64  & BEB & Western Grampians &&&&\\ 		
				16	& BB & West Coast VIC		&  & 65  & BEC & Bendigo Loddon &&&&\\
				17	& BC & East Coast VIC		&  & 66  & BED & Macedon &&&&\\
				18	& BC & North East VIC		&  & 67  & BEE & Spa Country &&&&\\
				19	& BD & North West VIC		&  & 68  & BEF & Ballarat &&&&\\
				20  & CA & Metro QLD			&  & 69  & BEG & Central Highlands &&&&\\
				21  & CB & Central Coast QLD	&  & 70  & CAA & Gold Coast &&&&\\
				22  & CC & North Coast QLD		&  & 71  & CAB & Brisbane &&&&\\
				23  & CD & Inland QLD			&  & 72  & CAC & Sunshine Coast &&&&\\
				24	& DA & Metro SA				&  & 73  & CBA & Central Queensland &&&&\\	
				25	& DB & South Coast SA		&  & 74  & CBB & Bundaberg &&&&\\	
				26	& DC & Inland SA			&  & 75  & CBC & Fraser Coast &&&&\\	
				27	& DD & West Coast SA		&  & 76  & CBD & Mackay &&&&\\

				28	& EA & West Coast WA 	& & 77  & CCA & Whitsundays &&&&\\	
				29	& EB & North WA			& & 78  & CCB & Northern &&&&\\	
				30	& EC & South WA 		& & 79  & CCC & Tropical North Queensland &&&&\\	
				31	& FA & South TAS		& & 80  & CDA & Darling Downs &&&&\\
				32	& FB & North East TAS	& & 81  & CDB & Outback &&&&\\	
				33	& FC & North West TAS	& & 82  & DAA & Adelaide &&&&\\
				34	& GA & North Coast NT	& & 83  & DAB & Barossa &&&&\\
				35	& GB & Central NT		& & 84  & DAC & Adelaide Hills &&&&\\
				\cmidrule(lr){1-3}
				\multicolumn{3}{c}{\textbf{Level 2 - Regions}} & & 85  & DBA & Limestone Coast &&&&\\
				\cmidrule(lr){1-3}
				36	& AAA & Sydney 			& 	& 86  & DBB & Fleurieu Peninsula &&&&\\
				37	& AAB & Central Coast	&	& 87  & DBC & Kangaroo Island &&&&\\
				38  & ABA & Hunter 			& 	& 88  & DCA & Murraylands &&&&\\
				39  & ABB & North Coast NSW & 	& 89  & DCB & Riverland &&&&\\
				40  & ABC & Hunter			& 	& 90  & DCC & Clare Valley &&&&\\
				41  & ACA & South Coast		& 	& 91  & DCD & Flinders Range and Outback &&&&\\
				42  & ADA & Snowy Mountains & 	& 92  & DDA & Eyre Peninsula &&&&\\
				43  & ADB & Capital Country & 	& 93  & DDB & Yorke Peninsula &&&&\\
				44  & ADC & The Murray 		& 	& 94  & EAA & Australia's Coral Coast &&&&\\
				45  & ADD & Riverina 		& 	& 95  & EAB & Experience Perth &&&&\\
				45  & AEA & Central NSW 	& 	& 96  & EAC & Australia's South West &&&&\\
				46  & AEB & New England North West &  & 97  & EBA & Australia's North West &&&&\\
				47  & AEC & Outback NSW & & 98  & ECA & Australia's Golden Outback &&&&\\
				\bottomrule
			\end{tabular}
		}
\end{table}

>>>>

\begin{table}[H]
	\caption{Geographical hierarchy of Australian tourism flow}\label{table:A1}
	\centering\tabcolsep=0.08cm
	\tiny
	\resizebox{\linewidth}{!}{
		\begin{tabular}{lllllllllll}
			\toprule
			\multicolumn{3}{c}{\textbf{Level 0 - Total}}    &&  \multicolumn{3}{l}{\textit{Regions cont.}}   &  & \multicolumn{3}{l}{\textit{Regions cont.}} \\
			\cmidrule(lr){1-3}
			1 & {\text{Tot}} & {Australia} &&  37	& AAB & Central Coast && 76  & CBD & Mackay   \\
			\cmidrule(lr){1-3}
			\multicolumn{3}{c}{\textbf{Level 1 - States}} && 38  & ABA & Hunter && 77  & CCA & Whitsundays\\
			\cmidrule(lr){1-3}
			2 & A & NSW 				&  & 39  & ABB & North Coast NSW   && 78  & CCB & Northern  \\
			3 & B & Victoria 			&  & 40  & ACA & South Coast  && 79  & CCC & Tropical North Queensland \\
			4 & C & Queensland 			&  & 41  & ADA & Snowy Mountains &&80  & CDA & Darling Downs   \\
			5 & D & South Australia     &  & 42  & ADB & Capital Country && 81  & CDB & Outback  \\
			6 & E & Western Australia   &  & 43  & ADC & The Murray   && 82  & DAA & Adelaide\\
			7 & F & Tasmania   			&  & 44  & ADD & Riverina  && 83  & DAB & Barossa\\
			8 & G & Northern Territory  &  & 45  & AEA & Central NSW &&  84  & DAC & Adelaide Hills \\
			\cmidrule(lr){1-3}
			\multicolumn{3}{c}{\textbf{Level 2 - Zones}}  &  &  46  & AEB & New England North West    &&85  & DBA & Limestone Coast\\
			\cmidrule(lr){1-3}
			9 	& AA & Metro NSW 	  	   	&  & 47  & AEC & Outback NSW   && 86  & DBB & Fleurieu Peninsula\\
			10 	& AB & North Coast NSW 	   	&  & 48  & AED & Blue Mountains  && 87  & DBC & Kangaroo Island\\
			11	& AC & South Coast NSW	   	&  & 49  & AFA & Canberra   &&88  & DCA & Murraylands \\
			12	& AD & South NSW 			&  & 50  & BAA & Melbourne &&89  & DCB & Riverland\\
			13	& AE & North NSW 			&  & 51  & BAB & Peninsula    &&90  & DCC & Clare Valley\\
			14	& AC & ACT					&  &  52  & BAC & Geelong  &&91  & DCD & Flinders Range and Outback \\
			15	& BA & Metro VIC			&  &  53  & BBA & Western   &&92  & DDA & Eyre Peninsula\\ 		
			16	& BB & West Coast VIC		&  &  54  & BCA & Lakes  && 93  & DDB & Yorke Peninsula\\
			17	& BC & East Coast VIC		&  &  55  & BCB & Grippsland    &&94  & EAA & Australia's Coral Coast\\
			18	& BC & North East VIC		&  &  56  & BCD & Phillip Island   && 95  & EAB & Experience Perth \\
			19	& BD & North West VIC		&  &  57  & BDA & Central Murray    &&96  & EAC & Australia's South West\\
			20  & CA & Metro QLD			&  & 58  & BDB & Goulburn    &&97  & EBA & Australia's North West \\
			21  & CB & Central Coast QLD	&  & 59  & BDC & High Country   &&98  & ECA & Australia's Golden Outback\\
			22  & CC & North Coast QLD		&  &  60  & BDD & Melbourne East &&99 & FAA & Hobert and South\\
			23  & CD & Inland QLD			&  &   61  & BDE & Upper Yarra &&100 & FBA & East Coast\\
			24	& DA & Metro SA				&  & 62  & BDF & Murray East  && 101 & FBB & Launceston, Tamar \& North\\	
			25	& DB & South Coast SA		&  &  63  & BEA & Wimmera+Mallee &&102 & FCA & North West\\	
			26	& DC & Inland SA			&  & 64  & BEB & Western Grampians &&103 & FCB& Wilderness West\\	
			27	& DD & West Coast SA		&  &65  & BEC & Bendigo Loddon  &&104 & GAA& Darwin\\

			28	& EA & West Coast WA 	& &  66  & BED & Macedon    &&105 & GAB& Kakadu Arnhem\\	
			29	& EB & North WA			& &  67  & BEE & Spa Country   && 106 & GAC& Katherine Daly\\	
			30	& EC & South WA 		& &   68  & BEF & Ballarat     &&107 & GBA& Barkly\\	
			31	& FA & South TAS		& &  69  & BEG & Central Highlands  &&108 & GBB& Lasseter\\
			32	& FB & North East TAS	& & 70  & CAA & Gold Coast  &&109 & GBC& Alice Springs\\	
			33	& FC & North West TAS	& & 71  & CAB & Brisbane  &&110 & GBD& MacDonnell\\
			34	& GA & North Coast NT	& & 72  & CAC & Sunshine Coast &&\\
			35	& GB & Central NT		& &  73  & CBA & Central Queensland      &&\\
			\cmidrule(lr){1-3}
			\multicolumn{3}{c}{\textbf{Level 2 - Regions}} & & 74  & CBB & Bundaberg    &&\\
			\cmidrule(lr){1-3}
			36	& AAA & Sydney 			& 	& 75  & CBC & Fraser Coast &&\\

			\bottomrule
		\end{tabular}
	}
\end{table}

### 2019-09-04 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Adding more references and adjusting table in Appendix

	Multivariate time series following an aggregation structure arise in many disciplines such as manufacturing, engineering, marketing and medicine\todo{include references}. Forecasts of these series should adhere to aggregation constraints to ensure aligned decision making. Earlier studies achieved this by only forecasting a single level of the hierarchy and then either aggregating in a bottom-up fashion \citep{Dunn1976} or disaggregating in a top-down fashion \citep{Gross1990, Athanasopoulos2009}.  For reviews of these approaches including a discussion of their advantages and disadvantages see \citet{Schwarzkopf1988, Kahn1998, Lapide1998, Fliedner2001}.

	In contrast to these methods, \cite{Hyndman2011} proposed forecasting all series in the hierarchy, referring to these as {\em base} forecasts.  Since base forecasts were produced independently they were not guaranteed to adhere to aggregation constraints and could thus be improved via further adjustment.  A framework was proposed whereby the base forecasts were assumed to follow a regression model.  The predicted values from this model were guaranteed to adhere to the linear constraints by construction and could thus be used as a new set of forecasts.  This approach and later modifications have subsequently been shown to outperform bottom-up and top-down approaches in a variety of empirical settings\todo{references}.

@@

	To establish the converse it suffices to postmultiply the condition $\bm{S}\bm{G}\bm{S}=\bm{S}$ by $\bm{G}$.  This yields $\bm{S}\bm{G}\bm{S}\bm{G}=\bm{S}\bm{G}$ which in turn implies idempotence since $(\bm{S}\bm{G})^2=\bm{S}\bm{G}$.
	\input{Appendix}
	\newpage

>>>>

	Multivariate time series following an aggregation structure arise in many sectors such as retail, energy, insurance, health and welfare and economics \citep{Karmy2019, Taieb2017, Almeida2016, JeoEtAl2019, Mahkya2017, LiTan2019, Shang2017}. Forecasts of these series should adhere to aggregation constraints to ensure aligned decision making. Earlier studies achieved this by only forecasting a single level of the hierarchy and then either aggregating in a bottom-up fashion \citep{Dunn1976} or disaggregating in a top-down fashion \citep{Gross1990, Athanasopoulos2009}.  For reviews of these approaches including a discussion of their advantages and disadvantages see \citet{Schwarzkopf1988, Kahn1998, Lapide1998, Fliedner2001}.

	In contrast to these methods, \cite{Hyndman2011} proposed forecasting all series in the hierarchy, referring to these as {\em base} forecasts.  Since base forecasts were produced independently they were not guaranteed to adhere to aggregation constraints and could thus be improved via further adjustment.  A framework was proposed whereby the base forecasts were assumed to follow a regression model.  The predicted values from this model were guaranteed to adhere to the linear constraints by construction and could thus be used as a new set of forecasts.  This approach and later modifications have subsequently been shown to outperform bottom-up and top-down approaches in a variety of empirical settings \citep{Hyndman2016, Athanasopoulos2009, Shang2017}.

@@

	To establish the converse it suffices to postmultiply the condition $\bm{S}\bm{G}\bm{S}=\bm{S}$ by $\bm{G}$.  This yields $\bm{S}\bm{G}\bm{S}\bm{G}=\bm{S}\bm{G}$ which in turn implies idempotence since $(\bm{S}\bm{G})^2=\bm{S}\bm{G}$.

	\input{Appendix}
	\newpage
